A Topography of Climate Change Research

### 2018-02-21 pres/2018_02_pres.tex
presentation updates

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}
\usepackage{framed}

@@

@@

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/volume_variety_bible_AR6}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\textbf{Topic Modelling}
		\begin{center}
			\begin{itemize}
				\item Topic modelling is a way of reducing the dimensionality of a corpus of documents
				\item A large matrix of documents x words is factorised by
				a matrix of topics x words and a matrix of topics x documents
			\citep{Lee1999}
				\item Topics describe the latent structure of the document corpus

@@

\textbf{Observations}
\begin{itemize}
	\item<5-> The size of the literature appears to be \textit{much} bigger than our estimate
	\item<6-> WG3 refers to more literature not directly about climate change, or not in peer-reviewed publications, than WG2, which refers to more than WG1
\end{itemize}

@@

@@

\begin{frame}{Preliminary results - structure}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}	
			\vspace*{-0.1\linewidth}
			\includegraphics[width=\linewidth]{../plots/network_wg_654}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
	%	\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

@@

%%%%%%%%

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

@@

\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}

@@

@@

\begin{frame}{Preliminary results - gaps in coverage}

@@

\begin{itemize}
	\item Each document \(d\) either matches or does not match an IPCC reference
	\item For each topic \(h\), we can sum the scores for each category of document
	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
\end{itemize}

@@

\begin{frame}{Preliminary results - gaps in coverage}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_topics_654.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Preliminary results - gaps in coverage}

			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_654.png}

@@

\begin{frame}{Preliminary results - gaps in coverage}

@@

\begin{frame}{Next steps}
	\begin{itemize}
		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
		\item Further analysis of new model
		\item (Manual) comparison of (AR6) topics with AR6 outline
	\end{itemize}
\end{frame}

>>>>

\usepackage[LGR,T1]{fontenc}
\usepackage[utf8]{inputenc} 
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}
\usepackage{framed}

@@

\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}

@@

\begin{frame}{Introduction}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\begin{figure}
			\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
			\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item<2-> Topography is a description of a landscape
				\item<3-> Topics (from the Greek \textgreek{τόπος}, place) can describe the features of body of text
			\end{itemize}
		\end{center}
	\end{column}
	\end{columns}
\end{frame}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess scientific literature on climate change 
			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/volume_variety_bible_AR6}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\textbf{Topic Modelling}
		\begin{center}
			\begin{itemize}
				\item Topic modelling is a way of reducing the dimensionality of a corpus of documents
				\item A large matrix of documents x words is factorised by
				a matrix of topics x words and a matrix of topics x documents
			\citep{Lee1999}
				\item Topics describe the latent structure of the document corpus (What is the matter?)

@@

\only<5->{\textbf{Observations}}
\begin{itemize}
	\item<5-> The size of the literature appears to be \textit{much} bigger than our estimate
	\item<6-> WG3 refers to more literature not directly about climate change, or not in peer-reviewed publications, than WG2, which refers to more than WG1
\end{itemize}

@@

\begin{frame}{Results}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}	
			\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\textbf{Outline}	
		\begin{center}
			\begin{itemize}
				\item<2-> Topography
				\item<3-> Structure
				\item<4-> Development
				\item<5-> Representation in past IPCC reports
				\item<6-> AR6 outlook
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Results - structure}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}	
			\vspace*{-0.1\linewidth}
			\includegraphics[width=\linewidth]{../plots/network_wg_654}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
	%	\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
		\begin{center}
			\begin{itemize}
				\item<1-> Topics describe comprehensible themes in climate change research
				\item<2-> Matching topics to the IPCC working group from which the majority of the topics are referenced in, a structure is generated based on topic-document correlations
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}

@@

\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}

@@

\begin{frame}{Results - Inter-working Group topics - WG 2 and 3}

@@

%%%%%%%%
%% RESULTS - DEVELOPMENT
%\begin{frame}{Results - Development}
%\only<1->{
%\begin{figure}
%	\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
%\end{figure}
%}
%\only<1->{
%	\centering
%	\textbf{Message}
%}
%\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{../plots/development/662_holocene}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Basic climate science topics are not as prominent as they were previously}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Sustainable development, and research agendas are more prominent}
}
\end{frame}

\begin{frame}
	The documents that underpin this growth
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.6\linewidth]{../plots/development/ar5_growth}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Fast growing topics in AR5 were on urban systems, negative emissions, buildings, consumption, biodiversity and risks}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/development/ar6_growth}	
\end{figure}
}
\only<1->{
	\centering
	\textbf{Negative emissions topics continue to grow,}
}
\end{frame}

%%%%%%%%%

@@

%\begin{frame}{Preliminary results - gaps in coverage}
%
%How can we get a sense of which topics are better covered in IPCC reports?
%
%\begin{itemize}
%	\item Each document \(d\) either matches or does not match an IPCC reference
%	\item For each topic \(h\), we can sum the scores for each category of document
%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
%\end{itemize}
%
%\end{frame}

\begin{frame}{Results - topic representation in IPCC reports}

@@

We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus

%\begin{itemize}
%	\item Each document \(d\) either matches or does not match an IPCC reference
%	\item For each topic \(h\), we can sum the scores for each category of document
%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
%\end{itemize}

@@

\begin{frame}{Results - topic representation in IPCC reports}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_all.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Results - topic representation in IPCC reports}

	\begin{figure}
			\includegraphics[width=0.8\linewidth]{../plots/ipcc_representation/ipcc_rep_662_ARs}
	\end{figure}

@@

\begin{frame}{Results - topic representation in IPCC reports}

@@

\begin{frame}{Results - AR6 outlook}

Outlines for the sixth assessment report have already been published.

The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a [simplified] topic score for each chapter.

These scores were summed and were compared to the corpus in general in the same way as with past reports

\begin{frame}{Results - topic representation in IPCC reports}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_AR6.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

%\begin{frame}{Next steps}
%	\begin{itemize}
%		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
%		\item Further analysis of new model
%		\item (Manual) comparison of (AR6) topics with AR6 outline
%	\end{itemize}
%\end{frame}
